Search for Spatially Extended Fermi-LAT Sources Using Two Years of Flight Data

### 2011-07-19 extended_catalog/paper/extended_catalog.tex
new plots

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of 1.5e-5 and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the 
Pass 7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

  \clearpage
  \begin{sidewaystable}
    \begin{centering}
%      \begin{tabular}{l|rrrrrrrr}
%        \hline
%        \hline
%        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
%        \hline
%        \multicolumn{9}{c}{$E > 1 \gev$} \\
%        \hline
%        2FGL J1627.0-2425c   &                154.9 &                131.0 &                102.4 &                     32.6 &                   21.1 &                 23.3 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
%        2FGL J1554.4-5317c   &                134.8 &                149.0 &                137.6 &                     39.4 &                   39.6 &                 39.8 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
%        2FGL J0823.0-4246    &                347.3 &                314.5 &                343.6 &                     66.1 &                   49.2 &                 56.6 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
%        \hline
%        \multicolumn{9}{c}{$E > 10 \gev$} \\
%        \hline
%        2FGL J1615.2-5138    &                 78.2 &                 77.6 &                 88.2 &                     46.4 &                   45.3 &                 53.7 & $  0.43\deg \pm   0.04\deg$ & $  0.53\deg \pm   0.03\deg$ \\
%        2FGL J1632.4-4753c   &                126.9 &                126.4 &                158.1 &                     64.0 &                   62.2 &                 94.1 & $  0.44\deg \pm   0.04\deg$ & $  0.67\deg \pm   0.03\deg$ \\
%        2FGL J2021.5+4026    &                236.5 &                221.2 &                265.8 &                    156.0 &                  140.6 &                162.6 & $  0.59\deg \pm   0.03\deg$ & $  0.72\deg \pm   0.03\deg$ \\
%        2FGL J1837.3-0700c   &                 45.5 &                 48.0 &                 39.2 &                     18.6 &                   20.9 &                 18.8 & $  0.35\deg \pm   0.08\deg$ & $  0.34\deg \pm   0.07\deg$ \\
%        2FGL J0851.7-4635    &                120.2 &                119.7 &                125.9 &                     90.1 &                   90.9 &                 94.7 & $  1.12\deg \pm   0.07\deg$ & $  1.16\deg \pm   0.08\deg$ \\
%        \hline
%      \end{tabular}
      \missingfigure{This analysis is still running\ldots}
      \label{alt_diff_model_results}
      \caption{
      This table shows a comparison of the \ts values gotten using \gtlike
      and \pointlike.  It also compares the fit values using the standard
      diffuse model and using the alternate diffuse model described
      in section~\ref{alt_diff_model_description}.  $\ts_\pointlike$
      is the \ts of the source fit with the extended hypothesis using
      \pointlike whereas $\ts_\gtlike$ is the same quantity using the
      same model but fitting with \gtlike.  There is good agreement
      between the two methods.
      }
    \end{centering}
  \end{sidewaystable}

>>>>

We simulated point sources of varying spectral models and fit them
them using \pointlike as both point and extended sources. The data was
simulated using \gtobssim\footnote{\gtobssim is distributed
by the Fermi Science Support Center (\cite{fssc}).}
The point sources were simulated with a power-law spectral model with
six $>100$ \mev fluxes ranging from $3\times 10^{-9} \ph/\cm^2/\sec$ to
$10^{-6} \ph/\cm^2/\sec$.  The point sources were simulated with spectral
indices ($\gamma$) of 1.5, 2, 2.5, and 3.  These values were picked to
to represent the types of sources detectable by the LAT.  The point
sources were simulated on top of an isotropic power-law background
with a Sreekumar-like spectrum ($>100$ \mev flux of $1.5\times 10^{-5}$ and spectral
index 2.1) (\cite{sreekumar_isotropic}).  The Monte Carlo simulation was
performed over a one year time interval using a default rocking profile
and a representative livetime fraction of 0.8.  The reconstruction was
performed with photons from an energy range of 1 \gev to 100 \gev using 4
energy bins per decade and using the 
Pass 7\_V6 (P7\_V6) Source Instrument
Response Function (IRFs).  For each point source, we used \pointlike
to fit it as both a point and extended source and calculate \tsext and
we only dept the sources which had a significant point source detection
($\ts>25$).

@@

  \clearpage
  \begin{sidewaystable}
    \begin{centering}
      \begin{tabular}{l|rrrrrrrr}
        \hline
        \hline
        Name                 &     $\ts_\pointlike$ &        $\ts_\gtlike$ &           $\ts_\alt$ &          \tsextpointlike &           \tsextgtlike &            \tsextalt &                    $\sigma$ &               $\sigma_\alt$ \\
        \hline
        \multicolumn{9}{c}{$E > 1 \gev$} \\
        \hline
        2FGL J0823.0-4246    &                347.3 &                314.7 &                343.9 &                     66.1 &                   46.1 &                 53.4 & $  0.37\deg \pm   0.03\deg$ & $  0.40\deg \pm   0.03\deg$ \\
        2FGL J1627.0-2425c   &                154.9 &                130.3 &                102.4 &                     32.6 &                   20.3 &                 23.8 & $  0.53\deg \pm   0.06\deg$ & $  0.39\deg \pm   0.04\deg$ \\
        2FGL J1554.4-5317c   &                134.8 &                150.8 &                139.4 &                     39.4 &                   37.6 &                 38.0 & $  0.52\deg \pm   0.04\deg$ & $  0.55\deg \pm   0.04\deg$ \\
        \hline
        \multicolumn{9}{c}{$E > 10 \gev$} \\
        \hline
        2FGL J0851.7-4635    &                120.2 &                120.0 &                126.1 &                     90.1 &                   76.7 &                 82.9 & $  1.12\deg \pm   0.07\deg$ & $  1.12\deg \pm   0.08\deg$ \\
        2FGL J1615.0-5051    &                 52.5 &                 54.0 &                 57.4 &                     17.5 &                   16.6 &                 12.4 & $  0.33\deg \pm   0.04\deg$ & $  0.33\deg \pm   0.04\deg$ \\
        2FGL J1615.2-5138    &                 76.2 &                 75.9 &                 89.4 &                     44.3 &                   47.6 &                 55.9 & $  0.42\deg \pm   0.03\deg$ & $  0.43\deg \pm   0.03\deg$ \\
        2FGL J1632.4-4753c   &                126.9 &                128.3 &                120.4 &                     64.0 &                   64.8 &                 63.7 & $  0.44\deg \pm   0.04\deg$ & $  0.44\deg \pm   0.04\deg$ \\
        2FGL J1837.3-0700c   &                 45.5 &                 47.0 &                 39.0 &                     18.6 &                   20.2 &                 16.6 & $  0.35\deg \pm   0.08\deg$ & $  0.35\deg \pm   0.07\deg$ \\
        2FGL J2021.5+4026    &                236.5 &                225.3 &                240.5 &                    156.0 &                  139.4 &                148.8 & $  0.59\deg \pm   0.03\deg$ & $  0.60\deg \pm   0.03\deg$ \\
      \end{tabular}
      \label{alt_diff_model_results}
      \caption{
      This table shows a comparison of the \ts values gotten using \gtlike
      and \pointlike.  It also compares the fit values using the standard
      diffuse model and using the alternate diffuse model described
      in section~\ref{alt_diff_model_description}.  $\ts_\pointlike$
      is the \ts of the source fit with the extended hypothesis using
      \pointlike whereas $\ts_\gtlike$ is the same quantity using the
      same model but fitting with \gtlike.  There is good agreement
      between the two methods.
      }
    \end{centering}
  \end{sidewaystable}
